\TheTitle

### 2017-07-14 paper/study.tex
Fixing the "commit sizes" sentence

We include two commits in the study to detect differences between \mt
sizes. The order that the commits are presented to each participant is
randomized. We analyzed the 15096 \mt{s} from April 16th 2005 to
October 14th 2014, which corresponds to the releases Linux 2.6.12-rc3
and Linux 3.17-rc1. 25\% of the trees contain at most a single commit
not including the root, while 50\% of the trees contain at most seven
non-root nodes. 75\% of the trees contain at least 51 nodes, and the
largest tree contains 7217 nodes.

@@

Table~\ref{tab:cross_commit_results} shows whether the \mtsize
has an effect on the three studied metrics. An interesting observation
from the figure is that the correctness for T5 and T9 are effected by
the size of the \mt, but the accuracy is not. The correctness
results for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9},
and the timing results for T7 are shown in Figure~\ref{fig:timing_t7}.

>>>>

We include two commits in the study to detect differences in the
correctness, accuracy, and timing between \mt sizes. The order that the
commits are presented to each participant is randomized. We analyzed the
15096 \mt{s} from April 16th 2005 to October 14th 2014, which
corresponds to the releases Linux 2.6.12-rc3 and Linux 3.17-rc1. 25\% of
the trees contain at most a single commit not including the root, while
50\% of the trees contain at most seven non-root nodes. 75\% of the
trees contain at least 51 nodes, and the largest tree contains 7217
nodes.

@@

Table~\ref{tab:cross_commit_results} shows whether the \mt size
has an effect on the three studied metrics. An interesting observation
from the figure is that the correctness for T5 and T9 are effected by
the size of the \mt, but the accuracy is not. The correctness
results for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9},
and the timing results for T7 are shown in Figure~\ref{fig:timing_t7}.
